---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  font-family: 'Arial', sans-serif;
  color: #333;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 10px;
}
```

## IC3 Study Environment Tracking

This report tracks observations of seat availability and noise levels in the IC3 study space. The data is collected through a Google Form and updated dynamically.

```{r data_processing}
library(tidyverse)
file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRkFZzJSUqhlUpl_1ivwLrWS3zQcWhlVfIyF-KC_Lhsbc6O3w4Mbp9x10NOvznU_efAe793qGk7aaAS/pub?output=csv"
logged_data <- read_csv(file)

latest_data <- logged_data %>%
  rename(
    free_seats = `How many seats are currently free in IC3? (enter a number between 0 and 200)`,
    activity = `What are the people around you doing in IC3?`,
    noise_level = `How would you describe the overall noise level around you in IC3?`,
    time_of_day = `What time of day is it?`
  )

avg_seats <- round(mean(latest_data$free_seats, na.rm = TRUE), 0)
total_obs <- nrow(latest_data)
min_seats <- min(latest_data$free_seats, na.rm = TRUE)
max_seats <- max(latest_data$free_seats, na.rm = TRUE)
```

### Observation Summary

So far, I have recorded `r total_obs` observations in the IC3 study area. On average, there are about `r avg_seats` free seats available when I visit, ranging from a low of `r min_seats` to a high of `r max_seats`.

### Noise Levels and Timing

The following charts show the distribution of noise levels and the times when these observations were recorded.

```{r charts}
ggplot(latest_data, aes(x = noise_level, fill = noise_level)) +
  geom_bar() +
  labs(title = "Distribution of Noise Levels", x = "Noise Description", y = "Count") +
  theme_minimal()

ggplot(latest_data, aes(x = time_of_day, fill = time_of_day)) +
  geom_bar() +
  labs(title = "Observations by Time of Day", x = "Time Period", y = "Count") +
  theme_minimal()
```
